Global Reach or Out of Reach

### 2019-05-10 Paper_markdown.Rmd
Test PDF produced

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms2.tex.url
title: "Global Reach or Out of Reach"
author: 
- name: Addison Huygens
  affiliation: University of Iowa
abstract: "Here's where you write 100 to 250 words, depending on the journal, that describe your objective, methods, results, and conclusion."
keywords: "Naval power hegemony"
date: "May 10, 2019"
fontsize: 12pt
spacing: single
bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), "bib$"))`}
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
---

\begin{document}

\begin{titlepage}

test

\end{titlepage}

@@

\end{document}

>>>>

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms2.tex
title: "Global Reach or Out of Reach"
author: 
- name: Addison Huygens
  affiliation: University of Iowa
abstract: "Here's where you write 100 to 250 words, depending on the journal, that describe your objective, methods, results, and conclusion."
keywords: "Naval power hegemony"
date: "May 10, 2019"
fontsize: 12pt
spacing: single
bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), "bib$"))`}
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
---

Test

@@
